Summary of models

### 2022-07-14 Models.Rmd
correlation and summary of models

---

@@

```{r, echo=FALSE, warning=FALSE,message=FALSE, figures-side, out.width="100%",fig.fullwidth=TRUE}

library(tidyverse)
#install.packages("broom.mixed")
library(broom.mixed)
library(broom)
#install.packages("lmerTest")
library(lmerTest)
library(dplyr)
library(knitr)
library(kableExtra)
library(patchwork)
library(ggcorrplot)

@@

df_with_plots <- a %>%
  group_by(Plant_gen_sp) %>%
  nest() %>%
  mutate(plot = map(data, function(.x) {
    .x  %>%
      cor() %>%
      ggcorrplot::ggcorrplot()
  }))

@@

plots1[[1]] + plots1[[2]] + plots1[[2]] + plots1[[2]]

@@

@@

@@

>>>>

header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
---

Data base from beefun: plant individuals per sites (13 sites) for five years (2015-2019). Data base has 400 observation, only matching individuals, some with no pollinator frequency (16 observations).
Fruit proportions, seed numbers and seed weight are calculated for each plant individual per plant species in site and year. Richness, visitation rate and frequency of pollinators are also calculated for plant individual per plant species. 
16 plant species but 4 are removed because they are present only one site.

@@

\blandscape

```{r, echo=FALSE, warning=FALSE,message=FALSE, figures-side,fig.height = 13,fig.width=18, out.width="100%",fig.fullwidth=TRUE}

library(tidyverse)
library(broom.mixed)
library(broom)
library(lmerTest)
library(dplyr)
library(knitr)
library(kableExtra)
library(patchwork)
library(ggcorrplot)
library(ggpubr)

@@

df_with_plots <- a %>%
  group_by(Plant_gen_sp) %>%
  nest() %>%
  mutate(plot = map(data, function(.x) {
    .x  %>%
      cor() %>%
      ggcorrplot::ggcorrplot(show.diag = F, type="lower",lab=TRUE,lab_size=4,tl.cex=12)
  }))

@@

ggarrange(plots1[[1]], plots1[[2]], plots1[[3]], plots1[[4]],plots1[[5]],plots1[[6]], plots1[[7]], plots1[[8]], plots1[[9]], plots1[[10]],plots1[[11]],plots1[[12]], ncol=4, nrow=3, common.legend = TRUE, legend="right")

@@

\elandscape

@@

\newpage
## Frequency

@@

## join together Lavandula species 
(L.peduncalata (49 obs) and L.stoechas (24 obs))

## Fruit proportion - richness

lavan_tog=Pollinator_Plant %>%
  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))

# richnes
ta_f_la<-lavan_tog %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~richness + (1|Site_ID),family=binomial,data)))%>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

ta_f_la<-ta_f_la %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

ta_f_la<-filter(ta_f_la, !term == "sd__(Intercept)")

ta_f_la %>% 
    kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(ta_f_la$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

## Fruit proportion - visitation rate

lavan_tog=Pollinator_Plant %>%
  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))

# visistation rate
ta_f2_la<-lavan_tog %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~visitatio_rate + (1|Site_ID),family=binomial,data)))%>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

ta_f2_la<-ta_f2_la %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

ta_f2_la<-filter(ta_f2_la, !term == "sd__(Intercept)")

ta_f2_la %>% 
    kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(ta_f2_la$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

## Fruit proportion - frequency

lavan_tog=Pollinator_Plant %>%
  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))

# frequency
ta_f3_la<-lavan_tog %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Frequency + (1|Site_ID),family=binomial,data)))%>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

ta_f3_la<-ta_f3_la %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

ta_f3_la<-filter(ta_f3_la, !term == "sd__(Intercept)")

ta_f3_la %>% 
    kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(ta_f3_la$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

## Seed number - richness

# richness
ta_seed_la<-lavan_tog %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(lmer(Seeds~richness+(1|Site_ID),data))) %>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

ta_seed_la<-ta_seed_la %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

ta_seed_la<-filter(ta_seed_la, !term == "sd__(Intercept)" & !term =="sd__Observation")

ta_seed_la %>% 
kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(7, bold = ifelse(ta_seed_la$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

## Seed number - visitation rate

# visistation rate
ta_seed2_la<-lavan_tog %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(lmer(Seeds~visitatio_rate+(1|Site_ID),data))) %>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

ta_seed2_la<-ta_seed2_la %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

ta_seed2_la<-filter(ta_seed2_la, !term == "sd__(Intercept)" & !term =="sd__Observation")

ta_seed2_la %>% 
kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(7, bold = ifelse(ta_seed2_la$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

## Seed number - frequency

# Frequency
ta_seed3_la<-lavan_tog %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(lmer(Seeds~Frequency+(1|Site_ID),data))) %>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

ta_seed3_la<-ta_seed3_la %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

ta_seed3_la<-filter(ta_seed3_la, !term == "sd__(Intercept)" & !term =="sd__Observation")

ta_seed3_la %>% 
kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(7, bold = ifelse(ta_seed3_la$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

## Seed weight - richness

# richnes
ta_weight_la<-lavan_tog %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(lmer(Seed_weight~richness+(1|Site_ID),data))) %>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

ta_weight_la<-ta_weight_la %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

ta_weight_la<-filter(ta_weight_la, !term == "sd__(Intercept)" & !term =="sd__Observation")

ta_weight_la %>% 
kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(7, bold = ifelse(ta_weight_la$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

## Seed weight - visitation rate

# visistation rate
ta_weight2_la<-lavan_tog %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(lmer(Seed_weight~visitatio_rate+(1|Site_ID),data))) %>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

ta_weight2_la<-ta_weight2_la %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

ta_weight2_la<-filter(ta_weight2_la, !term == "sd__(Intercept)" & !term =="sd__Observation")

ta_weight2_la %>% 
kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(7, bold = ifelse(ta_weight2_la$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

## Seed weight - frequency

# frequency
ta_weight3_la<-lavan_tog %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(lmer(Seed_weight~Frequency+(1|Site_ID),data))) %>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

ta_weight3_la<-ta_weight3_la %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

ta_weight3_la<-filter(ta_weight3_la, !term == "sd__(Intercept)" & !term =="sd__Observation")

ta_weight3_la %>% 
kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(7, bold = ifelse(ta_weight3_la$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")
